Constraints on the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1 from cosmic variance

### 2013-03-19 paper/ms.tex

\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the
  dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1
  from cosmic variance} 
\author[J.E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright Jaime E. Forero-Romero$^{1}$ and Julian Mejia$^{2}$}
\vspace*{6pt}\\
$^{1}$\\
$^{2}$
}

@@

>>>>

\title[Dark Matter Halo Mass for LAEs  at $z=3.1$]{Constraints on the
  dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1
  from cosmic variance} 
\author[J.E. Forero-Romero and J. Mejia]{
\parbox[t]{\textwidth}{\raggedright 
  Julian Mejia$^{2}$ and
Jaime E. Forero-Romero$^{1}$}
\vspace*{6pt}\\
$^{1}$\\
$^{2}$ Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia
}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_match_P5.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{./plots/Fig3_random_P5.pdf}\\
\end{center} 
\caption{$M_{\rm min}$-$M_{\rm max}$ plane for all models with
  $P>0.05$\label{figure:f_escape}.} 
\end{figure*}
